MSDS6372 - Final Project

### 2018-04-02 MSDS6372_Final_Project_BBHOF.Rmd
Added some text in the Intro and PCA

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# required libraries
library(kableExtra) # to make uber sexy tables for output
library(pastecs) # for easy descriptive statistics
library(ggbiplot) # implementation of biplot using ggplot2 for plotting PCs
library(Amelia) # cool library for exploring missing data
library(ROCR) # for ROC plots and AUC calculations

# turn off scientfic notation for the entire script
options(scipen = 999)

@@

@@

# display top 5 observations
knitr::kable(BBHOFRaw[1:5,],caption = "Top 10 Observations from Baseball Hall of Fame Data", row.names = FALSE, "html") %>%
  kable_styling(bootstrap_options = c("striped","hover"))

@@

# display number of NAs
sapply(BBHOFRaw, function(x) sum(is.na(x)))

@@

@@

# now selecting 90% of data as sample from total 'n' rows of the data  
sample <- sample.int(n=nrow(BBHOF_logistic), size=floor(.90*nrow(BBHOF_logistic)), replace=FALSE)

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# required libraries
library(kableExtra) # to make uber sexy tables for output
library(pastecs) # for easy descriptive statistics
library(ggbiplot) # implementation of biplot using ggplot2 for plotting PCs
library(Amelia) # cool library for exploring missing data
library(ROCR) # for ROC plots and AUC calculations
# turn off scientfic notation for the entire script
options(scipen = 999)
```

@@

Many players in the National Baseball League (MLB) become eligible for the National Baseball Hall of Fame after they have played 10 seasons of MLB and have been retired for five full seasons. For example, those players eligible for consideration in 2019 will have played their final game in 2013. However, many players who become eligible are not admitted.

This project will explore the career performance statistics that influence whether a player will be admitted into the National Baseball Hall of Fame. The core data set was procured from The American Statistical Association (http://ww2.amstat.org/publications/jse/datasets/MLBHOF.new.txt) and includes data assembled from The Baseball Encyclopedia (Reichler 1993) and Total Baseball (Thorn and Parmer 1993).

..

Finally, once we've established a model for determining whether a player will be admitted to the National Baseball Hall of Fame from the core data - we will make predictions on players that were not in the core data.

@@

# display top 5 observations
knitr::kable(BBHOFRaw[1:5,],caption = "Top 5 Observations from Baseball Hall of Fame Data", row.names = FALSE, "html") %>%
  kable_styling(bootstrap_options = c("striped","hover","condensed"))
```

# Missing Values in the Raw Data
The following is a graphical representation of the completeness of the data. It is also followed with a table of counts of NAs in the data. Fortunately, this data is very complete and the only features that are affected by NAs are: StolenBaseRuns, CaughtStealing, Strikeouts, and StolenBases.

@@

# calculate NAs for raw data, apply row labels as new column
NAdataframe <- sapply(BBHOFRaw, function(x) sum(is.na(x)))

# display NAs in kable table
knitr::kable(NAdataframe,caption = "Counts of NAs (Missing Values) in Raw Data", row.names = TRUE, "html") %>%
  kable_styling(bootstrap_options = c("striped","hover","condensed"), full_width=FALSE, position = "left")
```

#

@@

# Principal Components Analysis

@@

# now selecting 75% of data as sample from total 'n' rows of the data  
sample <- sample.int(n=nrow(BBHOF_logistic), size=floor(.75*nrow(BBHOF_logistic)), replace=FALSE)

@@

Future Eligible: https://baseballhall.org/hall-of-famers/future-eligibles
